### 2018-04-20 papers/synth/intro.tex
asd

We model a VTS as a labelled graph.
%
Each compartment of VTS is a node of the graph and and the
transport channels between the nodes is an edge.
%
The set of chemicals present in a compartment is the label of of
the compartment.
%
Similarly, the set of transported chemicals carried by an edge is the label
on the edge.
%
%

>>>>

We model a VTS as a labelled graph.
%
Each compartment of VTS is a node of the graph and and the
transport channels between the nodes is an edge.
%
The set of molecules present in a compartment is the label of
the compartment.
% 
Similarly, the set of transported molecules carried by an edge is the label
on the edge.
%
A molecule in a node or edge may be active or inactive. 
%
The constraints discussed on the VTSs that allow a VTS to be feasible
are combinatorial in nature, for example stability or 3-connectedness.
%
The problem of synthesizing parts of a VTS that are unobserved such that 
the modified VTS

It is appropriate that we translate 
We turn the problem of synthesizing parts of 
%
We consider several versions of the synthesis problem involving different
parts of VTSs that can be synthesized, such as modifying labels,
adding/deleting edges, learning activity functions, and adding nodes.
%
In order to synthesize the parts of a VTS such that it satisfies the constraints, 
we encode the synthesis problem into a satisfiability of QBF with uninterpreted
Boolean functions.

Since an available,

on the labels.
